As semiconductor scaling approaches its physical and economic limits, DTCO is becoming increasingly important, with TCAD serving as one of its key enabling tools. However, the main bottleneck in TCAD automation lies not in structure generation, but in the generation of Sdevice parameter files. While SDE is relatively structured, Sdevice parameterization requires simultaneous consideration of physical model selection, parameter tuning, material-specific domain knowledge, and literature-based interpretation. As a result, existing LLM- and SFT-based approaches can assist with simple code generation, but remain limited for physics-informed modeling. In this paper, we propose \textbf{PhysAgent}, which structures TCAD domain knowledge into an ontology based on the TCAD guide. By explicitly representing physical models, parameters, relationships, and constraints, the proposed framework supports physically consistent parameter generation and literature-driven modeling. This demonstrates that ontology-based knowledge structuring can enable expert-level TCAD automation even in data-scarce environments.As semiconductor scaling approaches its physical and economic limits, DTCO is becoming increasingly important, with TCAD serving as one of its key enabling tools. However, the main bottleneck in TCAD automation lies not in structure generation, but in the generation of Sdevice parameter files. While SDE is relatively structured, Sdevice parameterization requires simultaneous consideration of physical model selection, parameter tuning, material-specific domain knowledge, and literature-based interpretation. As a result, existing LLM- and SFT-based approaches can assist with simple code generation, but remain limited for physics-informed modeling. In this paper, we propose \textbf{PhysAgent}, which structures TCAD domain knowledge into an ontology based on the TCAD guide. By explicitly representing physical models, parameters, relationships, and constraints, the proposed framework supports physically consistent parameter generation and literature-driven modeling. This demonstrates that ontology-based knowledge structuring can enable expert-level TCAD automation even in data-scarce environments.