PhysAgent combines a TCAD physics ontology and literature-driven domain knowledge to guide LLM-based SDevice file generation. The constructed ontology is publicly available as an interactive web platform~\cite{ontology_tcad}.

\subsection{TCAD Physics Ontology}
An SDevice simulation takes a command file (\texttt{.cmd}) and a parameter file (\texttt{.par}) as input. The physics block in the \texttt{.cmd} file specifies the physical models activated for each material, while the \texttt{.par} file defines the parameters required by these models along with fundamental properties such as bandgap, permittivity, and the DOS effective masses of electrons and holes. Thus, the model selection in the \texttt{.cmd} file determines the parameter set that must be provided in the \texttt{.par} file.
To consistently capture this \texttt{.cmd}--\texttt{.par} dependency, we structure the relevant parameters, TCAD syntax, and physical knowledge into an ontology grounded in the governing equations of the physical models and the Poisson and transport equations. Each parameter is represented as a node, and nodes associated with the same physical model are grouped into an equation group. Node--equation and equation--equation relationships are encoded as edges and relations, from which the required parameter set is derived upon model selection. A syntax layer then applies the SDevice syntax to the selected equations and nodes to generate the \texttt{.cmd} and \texttt{.par} files ({\color{red}Fig.~\ref{fig:ontology}}).

\subsection{Ontology-Guided Generation}
Given a target device and material, PhysAgent accesses the ontology through an MCP (Model Context Protocol) interface that exposes four tools. \texttt{ontology\_overview} returns the node/edge map of the graph, serving as the entry point for grasping the overall structure. \texttt{get\_chapter} identifies the equation-level relations associated with a selected node and derives the parameter set required by the corresponding physical equations. \texttt{get\_reference} returns values and source citations for the derived parameters, drawn from a curated collection of papers, material datasheets, and TCAD references. Finally, \texttt{build\_syntax} assembles the selected equations and parameter values under the SDevice syntax to generate the final \texttt{.cmd} (Physics block) and \texttt{.par} files. In our experiments, we employ Claude Sonnet, whose context window is limited to 200k tokens, whereas the full ontology exceeds 400k tokens and therefore cannot be injected directly into the prompt. The MCP-based selective retrieval scheme circumvents this limitation by allowing the LLM to query only the information required at each step, keeping the per-query context well within the 200k-token budget. Moreover, each parameter in the generated \texttt{.par} inherits the citation returned by \texttt{get\_reference}, thereby enabling parameter-level provenance ({\color{red}Fig.~\ref{fig:framework}}).

\subsection{Ontology Expansion and Validation}
Unlike SFT-based approaches requiring retraining for new models or materials, PhysAgent uses a directional synchronization workflow with three artifact layers---Spec, Plan, and Impl---where changes propagate automatically from the source of truth while reverse modifications require explicit approval, ensuring incremental expansion without retraining.
